Technical Report

### 2018-03-21 fully-abstract-comp/technical-report.tex
Add reference.
Fix compilation.
added precondition to FTLR

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \ints \\
\com{r} &\in &  \tRegName \\
\com{\rn} &\defbnf &  \com{r} \mid n \\
\com{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\com{r}} \mid \tjnz{\com{r}}{\com{\rn}} \mid \tisptr{\com{r}}{\com{r}} \mid \tgeta{\com{r}}{\com{r}} \mid \tgetb{\com{r}}{\com{r}} \mid \\
      & &  \tgete{\com{r}}{\com{r}}\mid \tgetp{\com{r}}{\com{r}} \mid \tgetlin{\com{r}}{\com{r}} \mid \tmove{\com{r}}{\com{\rn}} \mid \tstore{\com{r}}{\com{r}} \mid\\
      & &  \tload{\com{r}}{\com{r}} \mid \tcca{\com{r}}{\com{\rn}} \mid \trestrict{\com{r}}{\com{\rn}} \mid \tlt{\com{r}}{\com{\rn}}{\com{\rn}} \mid \\
  & & \tplus{\com{r}}{\com{\rn}}{\com{\rn}} \mid \tminus{\com{r}}{\com{\rn}}{\com{\rn}} \mid \tsetatob{\com{r}} \mid \txjmp{\com{r}}{\com{r}} \mid \tcseal{\com{r}}{\com{r}} \mid \\ 
      & &   \tsplit{\com{r}}{\com{r}}{\com{r}}{\com{\rn}} \mid\tsplice{\com{r}}{\com{r}}{\com{r}} 
\end{array}
\]
$i$ defines the set $\Instr$

@@

The source machine is also a capability machine with memory capabilities and sealed capabilities. Unlike the target machine, the source machine has a built in stack along with special stack and return tokens used in place of the actual capabilities. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    o & \in & \nats \\
    \src{i} & \defbnf &  \com{i} \mid \scall{\offpc,\offsigma}{r}{r}
  \end{array}
\]
There is one syntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{\offpc,\offsigma}{}{}$ instruction (the $o$ refers to the seal it uses, namely the offset in the seals made available by linking).

@@

\subsection{Component layout and linking}
\dominique{21-3-2018: TODO: update this section (further) to reflect recent changes.}
A target- or source-level component needs a number of things.
In the following, we list what it needs followed by a description of how they are made available.

A program needs access to the following:
\begin{description}
\item[Code] The instructions of a component should of course be available so they can be executed.
\item[Component seals] Each call/return point of the component, as well as every location where new closures are created, needs a unique seal in order to enforce well-bracketedness.
  This seal needs to be unique on the entire machine.
\item[Stack] A component stores the value of local variables on the stack. 
\item[Persistent data storage] A component may also need to use "global variables" these are stored in a piece of memory separate from the stack.
\item[Access to other components' exported functions] A component may need to call other components.
  Every component makes available a number of exported values (e.g. sealed code-data pairs for invoking certain functions) and components are allowed to include these exported values in their data memory.
  They could, for example, keep a linking table there through which they can invoke other components' exports.
\end{description}

In the following, we describe the setup in detail.
Figure~\ref{fig:trg-prog-link} illustrates the setup (modulo the fact that the code memory contains a reference to the linking table, which is now no longer allowed).

The \emph{code} and \emph{program seals} are available through a normal read-execute capability in the $\pc$ register.
The program seals are stored as part of the code memory and can be accessed through the $\pc$ register.
The data memory may contain references to references exported by other components, organised, for example, as a linking table.
The remaining addresses governed by the capability in the $\pc$ register contain the instructions of the program.

@@

The \emph{persistent data storage} is expected to be accessible through a normal read-write capability in $r_\data$ during normal execution (during a return the stack capability will initially be in the $r_\data$ register, but it should be spliced with the returned stack and moved to the $r_\stk$ register). There are two ways for a program to get this data capability: (1) the data part of the code/data pair (for either a callback or a global function in the linking table) should be the sealed data capability. (2) During a call, the data capability should be stored on the stack, so it can be retrieved afterwards.
\begin{figure}
  \centering
  \includegraphics[angle=90,width=\textwidth]{img/linking.pdf}
  \caption{Linking and program layout (modulo the fact that the code memory contains a reference to the linking table, which is now no longer allowed).}
  \label{fig:trg-prog-link}
\end{figure}

@@

We define inductively when a component is valid ($\vdash \var{comp}$) by the below inference rules:
\begin{mathpar}
  \inference{
    \mscode(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\baddr} & [\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets \cup \sigcloss)
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \mscode(a) \in \ints\\
    \mscode([a \cdots a + \calllen-1]) = \scall[0..\calllen-1]{\offpc,\offsigma}{r_1}{r_2} \Rightarrow (\mscode(a+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr} \wedge \sigma_\baddr+\offsigma \in \sigrets)
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \exists d_\sigma : \dom(\mscode) \rightarrow \powerset{\Seal} \ldotp
    \sigrets = \biguplus_{a \in \dom(\mscode)} d_\sigma(a) \tand\\
    \forall a \in \dom(\mscode) \ldotp 
    d_\sigma(a),\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode
  }
  \and
  \inference{
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} z
  }
  \and
  \inference{
    c \in \overline{c_{\mathrm{import}}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{code}} & \perm \sqsubseteq \rx
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} ((\perm,\normal),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{data}} & \permbnf \sqsubseteq \rw&
    \lin = \linear \Rightarrow \emptyset \subset [\baddr,\eaddr] \subseteq A_{\mathrm{own}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} ((\perm,\lin),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \vsc \\
    \sigma \in \sigcloss
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \sealed{\sigma,\vsc}
  }
  \and
  \inference{
    \dom(\mscode) \mathrel{\#} \dom(\msdata)\\
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode \\
    \exists A_\mathrm{own} : \dom(\msdata) \rightarrow \powerset{\dom(\msdata)} & \dom(\msdata) = \biguplus_{a \in \dom(\msdata)} A_{\mathrm{own}}(a) \\
    \forall a \in \dom(\msdata)\ldotp \dom(\mscode),\dom(\msdata),A_{\mathrm{own}}(a),\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash \msdata(a)\\
    \overline{\dom(\mscode), \dom(\msdata), \emptyset, \overline{c_{\mathrm{import}}}, \sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c_{\mathrm{export}}}\\
  }{
    \vdash (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)
  }
\end{mathpar}

@@

\begin{definition}[Programs and Contexts]
  We define a program as a $(\var{comp}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$ component with an empty import list and $c_{\mathrm{main},c}$ and $c_{\mathrm{main},d}$ are two of the exported symbols.

  Given a component $\var{comp}$, a context is a tuple $(\var{comp'}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$ such that $\var{comp'}$ is a component and $(\var{comp} \bowtie \var{comp'}, c_{\mathrm{main},c}, c_{\mathrm{main},d})$ is a program.
\end{definition}

\begin{definition}[Initial execution configuration]
  \begin{mathpar}
    \inference{
      \reg(\pc) = c_{\mathrm{main},c} & 
      \reg(\rdata) = c_{\mathrm{main},d} \\
      \src{\reg(\rstk) = \stkptr{\rx,\baddr_\stk,\eaddr_\stk,\eaddr_\stk}} & 
      \trg{\reg(\rstk) = ((\rx,\linear),\baddr_\stk,\eaddr_\stk,\eaddr_\stk)} \\
      \mem = \mscode \uplus \msdata \trg{\;\uplus\; \ms_\stk} \\
      [\baddr_\stk,\eaddr_\stk] = \dom(\ms_\stk ) \mathrel{\#} (\dom(\mscode) \cup \dom(\msdata)) &
      \overline{c_{\mathrm{import}}} = \emptyset
    }{
      ((\mscode, \msdata, \overline{c_{\mathrm{import}}}, \overline{c_{\mathrm{export}}}, \sigrets, \sigcloss),  c_{\mathrm{main},c}, c_{\mathrm{main},d}) \rightsquigarrow (\mem, \reg\src{, \emptyset, \ms_\stk})
    }
  \end{mathpar}
\end{definition}

\section{Compiler}
\label{sec:compiler}
\[
\comp{\cdot} : \src{i}^* \fun \com{i}^*
\]
\dominique{27-09-2017: Regarding the type signature for $[\cdot]$ above: does this mean that it maps lists of instructions to lists of instructions? Is there another function that compiles a single instruction to a list of instructions?}
\lau{28-09-2017: Yes, that was the thought at the moment, but this may very well change soon. This compiler would then use a compiler that compiles single instructions. That said, this part was added a long time ago and for some reason (some details about the compilation probably did not make sense to me at the moment), I did not complete it. I think the compiler will probably change to be from programs to programs, and a programs is not just going to be a list of instructions.}

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
% Note: the below FTLR is simpler than the above thanks to the new expression relation relating pairs of caps rather than pairs of pairs of caps. It expresses that any reasonable executable capability is safe to use as the pc capability. 
\begin{theorem}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If
  \begin{itemize}
  \item $\npair{(\baddr,\eaddr)} \in \readCond{\lin,W}$
  \item $\npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{itemize}
  \item \begin{itemize}
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\trust = \trusted$
    \item the compilation assumptions on $n$, $W$, ...
    \item the full abstraction conditions (difference with the previous point?)
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \item $\trust = \untrusted$
    \end{itemize}
  \end{itemize}
  Then
  \[
    \npair{\left(\arraycolsep=0pt\array{l}((\rx,\lin),\baddr,\eaddr,\aaddr),\\
      ((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \in \lreg{\trust}(W)
  \]
  \dominique{6-3-2018: I added $\xReadCond{\lin,W}$ since we are assuming there are no rwx pointers anywhere.}
  \begin{definition}[The compilation assumptions]
    No call uses $\rtmp{1}$ for jumping.\\
    ...
  \end{definition}

>>>>

\subsection{Syntax}
\label{sec:syntax}
The target machine is a simple capability machine with memory capabilities and sealed capabilities\footnote{In previous work, we used enter capabilities but for this the complexity introduced by mixing writable and executable memory is difficult to handle.} (inspired by CHERI). The syntax of the instructions of the target machine is defined as follows:
\[
\begin{array}{rcl}
n &\in & \ints \\
\trg{r} &\in &  \tRegName \\
\trg{\rn} &\defbnf &  \trg{r} \mid n \\
\trg{i} &\defbnf & \tfail \mid \thalt \mid \tjmp{\trg{r}} \mid \tjnz{\trg{r}}{\trg{\rn}} \mid \tisptr{\trg{r}}{\trg{r}} \mid \tgeta{\trg{r}}{\trg{r}} \mid \tgetb{\trg{r}}{\trg{r}} \mid \\
      & &  \tgete{\trg{r}}{\trg{r}}\mid \tgetp{\trg{r}}{\trg{r}} \mid \tgetlin{\trg{r}}{\trg{r}} \mid \tmove{\trg{r}}{\trg{\rn}} \mid \tstore{\trg{r}}{\trg{r}} \mid\\
      & &  \tload{\trg{r}}{\trg{r}} \mid \tcca{\trg{r}}{\trg{\rn}} \mid \trestrict{\trg{r}}{\trg{\rn}} \mid \tlt{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \\
  & & \tplus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tminus{\trg{r}}{\trg{\rn}}{\trg{\rn}} \mid \tsetatob{\trg{r}} \mid \txjmp{\trg{r}}{\trg{r}} \mid \tcseal{\trg{r}}{\trg{r}} \mid \\ 
      & &   \tsplit{\trg{r}}{\trg{r}}{\trg{r}}{\trg{\rn}} \mid\tsplice{\trg{r}}{\trg{r}}{\trg{r}} 
\end{array}
\]
$i$ defines the set $\Instr$

@@

The source machine is also a capability machine with memory capabilities and sealed capabilities. Unlike the target machine, the source machine has a built in stack along with special stack and return tokens used in place of the actual capabilities. The syntax of the source machine language is as follows:
\[
  \begin{array}{rcl}
    o & \in & \nats \\
    \src{i} & \defbnf &  \trg{i} \mid \scall{\offpc,\offsigma}{r}{r}
  \end{array}
\]
There is one syntactic difference between the source language and the target language, namely the target language has an extra instruction in the $\scall{\offpc,\offsigma}{}{}$ instruction (the $o$ refers to the seal it uses, namely the offset in the seals made available by linking).

@@

\subsection{Component layout and linking}
We define a notion of

A target-level program needs a number of things available in order to be able to execute securely. In the following, we list what it needs followed by a description of how they are made available.

A program needs access to the following:
\begin{description}
\item[Code] The instructions of a program should of course be available so they can be executed.
\item[Program seals] Each call/return point of the program needs a unique seal in order to enforce well-bracketedness. This seal needs to be unique on the entire machine.
\item[Stack] A program stores the value of local variables on the stack. 
\item[Persistent data storage] A program may also need to use "global variables" these are stored in a piece of memory separate from the stack.
\item[Linking table] A program may need to call other programs. Other programs are made available in a linking table.
\end{description}

In the following, we describe the setup in detail. Figure~\ref{fig:trg-prog-link} illustrates the setup.

The \emph{code}, \emph{program seals}, and \emph{linking table} are available through a normal read-execute capability in the $\pc$ register. The program seals are found on the first address governed by this capability. The second address governed by the capability contains a normal read capability that governs the linking table and points to the first address. The remaining addresses governed by the capability in the $\pc$ register contain the instructions of the program.

@@

The \emph{persistent data storage} is expected to be accessible through a normal read-write capability in $r_\data$ during normal execution (during a return the stack capability will initially be in the $r_\data$ register, but it should be spliced with the returned stack and moved to the $r_\stk$ register). There are two ways for a program to get this data capability: (1) the data part of the code/data pair (for either a callback or a global function in the linking table) should be the sealed data capability. (2) During a call, the data capability should be stored on the stack, so it can be retrieved afterwards.
\begin{figure}
  \centering
  \includegraphics[angle=90,width=\textwidth]{img/linking.pdf}
  \caption{Linking and program layout.}
  \label{fig:trg-prog-link}
\end{figure}

@@

We define inductively when a component is valid ($\vdash \var{comp}$) by the below inference rules:
\begin{mathpar}
  \inference{
    \mscode(a) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr} & [\sigma_\baddr,\sigma_\eaddr] \subseteq (\sigrets \cup \sigcloss)
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \mscode(a) \in \ints\\
    \mscode([a \cdots a + \calllen-1]) = \scall[0..\calllen-1]{\offpc,\offsigma}{r_1}{r_2} \Rightarrow (\mscode(a+\offpc) = \seal{\sigma_\baddr,\sigma_\eaddr,\sigma_\aaddr} \wedge \sigma_\baddr+\offsigma \in \sigrets)
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }
  \and
  \inference{
    \exists d_\sigma : \dom(\mscode) \rightarrow \powerset{\Seal} \ldotp
    \sigrets = \biguplus_{a \in \dom(\mscode)} d_\sigma(a) \tand\\
    \forall a \in \dom(\mscode) \ldotp 
    d_\sigma(a),\sigcloss \vdash_{\mathrm{comp-code}} \mscode,a
  }{
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode
  }
  \and
  \inference{
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} z
  }
  \and
  \inference{
    c \in \overline{c_{\mathrm{import}}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{code}} & \perm \sqsubseteq \rx
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} ((\perm,\normal),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    [\baddr,\eaddr] \subseteq A_{\mathrm{data}} & \permbnf \sqsubseteq \rw&
    \lin = \linear \Rightarrow \emptyset \subset [\baddr,\eaddr] \subseteq A_{\mathrm{own}}
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} ((\perm,\lin),\baddr,\eaddr,\aaddr)
  }
  \and
  \inference{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \vsc \\
    \sigma \in \sigcloss
  }{
    A_{\mathrm{code}},A_{\mathrm{data}},A_{\mathrm{own}},\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash_{\mathrm{comp-value}} \sealed{\sigma,\vsc}
  }
  \and
  \inference{
    \dom(\mscode) \mathrel{\#} \dom(\msdata)\\
    \sigrets,\sigcloss \vdash_{\mathrm{comp-code}} \mscode \\
    \exists A_\mathrm{own} : \dom(\msdata) \rightarrow \powerset{\dom(\msdata)} & \dom(\msdata) = \biguplus_{a \in \dom(\msdata)} A_{\mathrm{own}}(a) \\
    \forall a \in \dom(\msdata)\ldotp \dom(\mscode),\dom(\msdata),A_{\mathrm{own}}(a),\overline{c_{\mathrm{import}}},\sigrets,\sigcloss \vdash \msdata(a)\\
    \overline{\dom(\mscode), \dom(\msdata), \emptyset, \overline{c_{\mathrm{import}}}, \sigrets,\sigcloss \vdash_{\mathrm{comp-value}} c_{\mathrm{export}}}\\
  }{
    \vdash (\mscode,\msdata,\overline{c_{\mathrm{import}}},\overline{c_{\mathrm{export}}},\sigrets,\sigcloss)
  }
\end{mathpar}

@@

\begin{definition}[Programs and Contexts]
  We define a program as a $(\var{comp},c_{\mathrm{main}})$ component with an empty import list and $c_{\mathrm{main}}$ is one of the exported symbols.

  Given a component $\var{comp}$, a context is a tuple $(\var{comp'},c_{\mathrm{main}})$ such that $\var{comp'}$ is a component and $(\var{comp} \bowtie \var{comp'},c_{\mathrm{main}})$ is a program.
\end{definition}

\section{Compiler}
\label{sec:compiler}
\[
\comp{\cdot} : \src{i}^* \fun \trg{i}^*
\]
\dominique{27-09-2017: Regarding the type signature for $[\cdot]$ above: does this mean that it maps lists of instructions to lists of instructions? Is there another function that compiles a single instruction to a list of instructions?}
\lau{28-09-2017: Yes, that was the thought at the moment, but this may very well change soon. This compiler would then use a compiler that compiles single instructions. That said, this part was added a long time ago and for some reason (some details about the compilation probably did not make sense to me at the moment), I did not complete it. I think the compiler will probably change to be from programs to programs, and a programs is not just going to be a list of instructions.}

@@

% \dominique{22-1-2018: the below is an alternative proposal to the above definition. It is part of a proposed refactoring to simplify the merge the cases for return pointers and closures in the value relation.}
% Note: the below FTLR is simpler than the above thanks to the new expression relation relating pairs of caps rather than pairs of pairs of caps. It expresses that any reasonable executable capability is safe to use as the pc capability. 
\begin{theorem}[FTLR]
  \label{thm:ftlr}
  For all $n,W,\lin,\baddr,\eaddr,\aaddr$,
  If
  \begin{itemize}
  \item $\npair{(\baddr,\eaddr)} \in \readCond{\lin,W}$
  \item $\npair{(\baddr,\eaddr)} \in \xReadCond{\lin,W}$
  \end{itemize}
  and one of the following sets of requirements holds:
  \begin{itemize}
  \item \begin{itemize}
    \item $[\baddr,\eaddr] \subseteq \ta$
    \item $\trust = \trusted$

    \item For all $\npair{\stpair{\reg}{\reg}} \in \lrrtrusted(W)$ and $\memSat{\src{\ms_S},\src{\ms_\stk},\src{\stk},\ms_T}{W}$ and $\ms_f$, we have $\src{\Phi} = (\src{\ms_S} \uplus \ms_f, \src{reg_S}, \src{\stk}, \src{\ms_\stk})$ and 
      \[
        \sigrets = \bigcup_{r \in \dom(\pwheap)} \{\sigma \mid \pwheap(r) = \codereg{\ta',\sigrets',\_} \wedge \sigma \in \sigrets'  \wedge \ta' \subseteq \ta\}
      \]
      and
      \[
        \sigcloss = \bigcup_{r \in \dom(\pwheap)} \{\sigma \mid \pwheap(r) = \codereg{\ta',\_,\sigcloss'} \wedge \sigma \in \sigcloss'  \wedge \ta' \subseteq \ta\}
      \]
      \begin{itemize}           
\item $\Phi$ checks $\stkb$ before calls in $\ta$ for $n$ steps (Definition~\ref{def:check-stack-addr-before-call}).
  \item $\Phi$ uses link seals properly in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:use-return-seals-call}).
  \item $\Phi$ handle trusted seals properly in $\ta$ with components parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:handle-trusted-seals-properly}).
  \item $\Phi$ does not store link seals and code capabilities in $\ta$ with component parameters $\sigrets$ and $\sigcloss$ for $n$ steps (Definition~\ref{def:never-store-seal-code-cap}).
      \end{itemize}
    \end{itemize}
  \item
    \begin{itemize}
    \item $[\baddr,\eaddr] \mathrel{\#} \ta$
    \item $\trust = \untrusted$
    \end{itemize}
  \end{itemize}
  Then
  \[
    \npair{\left(\arraycolsep=0pt\array{l}((\rx,\lin),\baddr,\eaddr,\aaddr),\\
      ((\rx,\lin),\baddr,\eaddr,\aaddr)\endarray\right)} \in \lreg{\trust}(W)
  \]
  \dominique{6-3-2018: I added $\xReadCond{\lin,W}$ since we are assuming there are no rwx pointers anywhere.}
  \begin{definition}[The compilation assumptions]
    No call uses $\rtmp{1}$ for jumping.\\
    ...
  \end{definition}
